---
title: "Database_Cantones"
author: "Garro"
date: "2024-02-15"
output: html_document
---

Reading the data from the google sheet:

```{r}
library(tidyverse)
library(pdftools)
library(tesseract)

no_plan <- read.csv("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Hertie-Thesis/PDF_Processing/parties_with_no_plan.csv")

head(no_plan)
``` 
Ahora a leer los textos de los documentos y sus nombres

```{r}
setwd("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024")
#names of the files
dirs <- list.dirs("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Propuestas de planes")
#drop general files and only keep specifc ones
dirs <- dirs[-c(1,2,19,28,40,51,58,72)]
files_dirs <- c()

for (i in dirs){
  files_in_folder = list.files(i)
  files = c(paste0(i,"/",files_in_folder))
  files_dirs = c(files_dirs, files)
}
# Ich lese die dateien -> I read the files
# Kommentar, entkommentar -> Comment, un comment
# Programme laufen lassen -> Run a script (Program run let)

#
data <- data.frame(files_dirs)

names(data) <- "Location"

data <- cbind(data$Location,data.frame(str_split_fixed(data$Location,"\\/",13)[,11:13]))

names(data) <- c("Location","Provincia","Municipalidad","Partido")

data <- data %>% mutate(Partido = str_sub(Partido,1,(str_locate(Partido,"\\.")[,1]-1)))
head(data)
```


```{r}

#read PDF
#mini test 

#data_test <- data[sample(nrow(data), 12), ]

#try(pdf_text(data$Location[53]))
#c(5,41,286,334,)

#for(i in 335:340){
#  print(i)
#  pdf_text(data$Location[i])
#}

numbers <-seq(1:340)
numbers <- numbers[-c(5,41,286,334)]
data$Text = NA

data[c(5,41,286,334),]

for(i in numbers){
  text = list(pdf_text(data$Location[i]))
  data$Text[i] = text
}

data$Location[c(5,41,286,334)]
```


```{r}
plans <- no_plan %>% select(-c(plan_link,doble_check)) %>% 
  mutate(Provincia = str_replace_all(toupper(Privincia)," ","_"),
         Canton = str_replace_all(toupper(Canton)," ","_"),
         Partido = str_replace_all(toupper(Partido)," ","_"))

plans <- plans %>% mutate(Municipalidad = Canton, Location = NA, Text = NA) %>% 
  select(-Canton)

#names(plans);names(data[,c(4,2,3,1,5)])

#join both datasets
plans <- rbind(plans[,c(4,2,3,1,5)],data)


#View(plans)
```

Add the candidates and the winners, with these variables
Cédula	
Nombre del Candidato	
Puesto	
Partido	
Provincia	Canton	
Ganador	
Votos	
Participacion	
Abstencionismo
Tipo de documento

Documents in the following database that have a "Good" in the document column are those that are readable with R

```{r}
library(readxl)
library(stringi)

candidatos <- read_xlsx("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/alcaldes_para_R.xlsx")

names(candidatos) <- c("Cedula","Candidato","Puesto","Partido","Provincia","Municipalidad","Ganador","Votos","Participacion","Abstencionismo","Tipo_Documento")

cn <- candidatos %>% select(Provincia, Municipalidad, Partido, Candidato, Ganador, Votos, Participacion, Abstencionismo, Tipo_Documento) %>% 
  mutate(Provincia = stri_trans_general(str_replace_all(toupper(Provincia)," ","_"), "Latin-ASCII"),
         Municipalidad = stri_trans_general(str_replace_all(toupper(Municipalidad)," ","_"), "Latin-ASCII"),
         Partido = stri_trans_general(paste0("PARTIDO_",str_replace_all(toupper(Partido)," ","_")), "Latin-ASCII")
         )


#stringi::stri_trans_general(x, "Latin-ASCII")

plans <- plans %>% full_join(cn,by=c("Provincia","Municipalidad","Partido"))

plans

```

OCR
No sirvio ): no son datos buenos, mejor dejarlos ir.
```{r}
ns <- which(plans$Tipo_Documento == "OCR")
#235, 252, 266, 281, 290, 298, 318, 353, 360, 372, 373, 388, 389, 441, 442, 454, 467, 469, 527, 529, 541, 555, 561

plans[ns,5] <- NA
plans[ns,5]


#plans[ns,c(2,3,4)]
#(plans$Location[252])
#convert into 
#pdf_convert(PDF_folder,output_folder,dpi = 600)
#pdf_convert(plans$Location[235],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/235"
#list.files("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/235")

#tx <- c()
#for(i in list.files("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/235")){
#  texto = ocr(paste0("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/235/",i))
#  tx <- c(tx,texto)
#}
#plans$Text[235] <- tx

#tx <- c()
#for(i in list.files("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/290")){
#  texto = ocr(paste0("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/290/",i))
#  tx <- c(tx,unlist(texto))
  #print(texto)
#}

#tx

#pdf_convert(plans$Location[252],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/252"


#tx <- c()
#for(i in list.files("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/252")){
#  texto = ocr(paste0("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/252/",i))
#  tx <- c(tx,texto)
#}
#plans$Text[252] <- tx

#pdf_convert(plans$Location[266],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/266"



#tx <- c()
#for(i in list.files("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/")){
#  texto = ocr(paste0("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/num/",i))
#  tx <- c(tx,texto)
#}
#plans$Text[num] <- tx

#pdf_convert(plans$Location[281],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/281"
#tx <- c()
#for(i in list.files("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/num")){
#  texto = ocr(paste0("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/num/",i))
#  tx <- c(tx,texto)
#}

#plans$Text[num] <- tx
#pdf_convert(plans$Location[290],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/290"

#pdf_convert(plans$Location[298],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/298"

#pdf_convert(plans$Location[318],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/318"

#pdf_convert(plans$Location[353],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/353"

#pdf_convert(plans$Location[360],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/360"

#pdf_convert(plans$Location[372],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/372"

#pdf_convert(plans$Location[373],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/373"

#pdf_convert(plans$Location[388],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/388"

#pdf_convert(plans$Location[389],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/389"

#pdf_convert(plans$Location[441],dpi = 600) 
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/441"

#pdf_convert(plans$Location[442],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/442"

#pdf_convert(plans$Location[454],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/454"

#pdf_convert(plans$Location[467],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/467"

#pdf_convert(plans$Location[469],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/469"

#pdf_convert(plans$Location[527],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/527"

#pdf_convert(plans$Location[529],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/529"

#pdf_convert(plans$Location[541],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/541"

#pdf_convert(plans$Location[555],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/555"

#pdf_convert(plans$Location[561],dpi = 600)
# "C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/561"


#tx <- c()
#for(i in list.files("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/290")){
#  texto = ocr(paste0("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/290/",i))
#  tx <- c(tx,unlist(texto))
  #print(texto)
#}




#ns <- which(plans$Tipo_Documento == "OCR")
#ns <-  c(281,290)
#for (i in ns){
#  tx <- c()
#  for(j in list.files(paste0("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/",as.character(i)))){
#    texto = ocr(paste0("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/",as.character(i),"/",as.character(j)))
#    tx <- c(tx,unlist(texto))
#  }
#  plans$Text[i] <- list(tx)
  #print(paste0(i,list(tx)))
#}


#ns <- which(plans$Tipo_Documento == "NO SE")
# 227 263 508 556
#plans[ns,c(2,3,4)]
#pdf_convert(plans$Location[227],dpi = 600)
#pdf_convert(plans$Location[263],dpi = 600)
#pdf_convert(plans$Location[508],dpi = 600)
#pdf_convert(plans$Location[556],dpi = 600)

#for (i in ns){
#  print(c(i,plans$Text[i]))}



#for(i in ns){
#  print(paste0(i, plans$Text[i]))
#}

```

Los raros que se pueden copy paste

```{r}

ns <- which(plans$Tipo_Documento == "NO SE")
for (i in ns){
  for(j in list.files(paste0("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/",as.character(i)))){
    texto = list(pdf_text(paste0("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/Planes_OCR/",as.character(i),"/",as.character(j))))
  }
  plans$Text[i] <- texto
  #print(paste0(i,list(tx)))
}

```



```{r}
saveRDS(plans, file = "plans.rds")

data <- readRDS("C:/Users/carme/Dropbox/MIO/DOCS/Hertie/Thesis/Elecciones_Municipales_2024/plans.rds")

#View(plans)
```









